Implications of afforestation policies for global markets

### 2024-02-27 paper.Rmd
Update paper.Rmd

The global gains that can be realized from afforestation, however, are uncertain, with broad estimates of cumulative sequestration ranging from 42 gigatonnes to 700 gigatonnes by the end of the century [@veldman2019]  [@bastin2019]  [@humpenoder2014]  [@sathaye2006]  [@doelman2020]. In addition, the amount of land conversion that would be required also varies greatly, with estimates ranging from 0.3 billion hectares to 2.8 billion hectares [@veldman2019]  [@bastin2019]  [@humpenoder2014]  [@doelman2020]. In many cases, these results suggest massive losses in the amount of pasture and cropland that would be available. This puts into question the feasibility of attaining these results, as almost 90 percent of deforestation worldwide is undertaken to expand the amount of agricultural land [@fao2021]. There are many reasons for this. For example, as nations develop and disposable incomes rise, consumers often change to more meat-based diets. Population growth is also a driver and when it is especially high, which is the case at present throughout most of Africa, this also puts pressure on policymakers to allow greater conversion of forestland into farmland. Still, previous research has suggested that substantive gains in the carbon sink (+23.8PgCo2e/yr) can be made without sacrificing agricultural land [@griscom2017].

>>>>

The global gains that can be realized from afforestation, however, are uncertain, with broad estimates of cumulative sequestration ranging from 42 gigatonnes to 700 gigatonnes by the end of the century [@veldman2019]  [@bastin2019]  [@humpenoder2014]  [@sathaye2006]  [@doelman2020]. In addition, the amount of land conversion that would be required also varies greatly, with estimates ranging from 0.3 billion hectares to 2.8 billion hectares [@veldman2019]  [@bastin2019]  [@humpenoder2014]  [@doelman2020]. In many cases, these results suggest massive losses in the amount of pasture and cropland that would be available. This puts into question the feasibility of attaining these results, as almost 90 percent of deforestation worldwide is undertaken to expand the amount of agricultural land [@fao2021]. There are many reasons for this. For example, as nations develop and disposable incomes rise, consumers often change to more meat-based diets. Population growth is also a driver. Currently, the United Nations' medium variant population projections suggest that between 2023 and 2033 the worlds' population will grow by 8.8 percent, a gain of 707.1 million people [@un2024]. And where population growth is especially high, which is the case at present throughout most of Africa (2023-2033 population growth: 25.0%: 360.6 million), this puts extreme pressure on policymakers to allow greater conversion of forestland into farmland. Still, some research has suggested that substantive gains in the carbon sink (+23.8PgCo2e/yr) can be made without sacrificing agricultural land [@griscom2017].
